### 2025-07-04 multiple-regression.qmd
20250704 - effect sizes

summary(linearRegression)
```

@@

summary(logisticRegression)
```

@@

summary(ordinalRegression)
```

@@

summary(poissonRegression)
```

@@

summary(negativeBinomialRegression)
```

>>>>

summary(linearRegression)
print(effectsize::standardize_parameters(linearRegression, method = "refit"), digits = 2)
```

@@

summary(logisticRegression)
print(effectsize::standardize_parameters(logisticRegression, method = "refit"), digits = 2)
```

@@

summary(ordinalRegression)
print(effectsize::standardize_parameters(ordinalRegression, method = "refit"), digits = 2)
```

@@

summary(poissonRegression)
print(effectsize::standardize_parameters(poissonRegression, method = "refit"), digits = 2)
```

@@

summary(negativeBinomialRegression)
print(effectsize::standardize_parameters(negativeBinomialRegression, method = "refit"), digits = 2)
```
